---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# skewsamp

<!-- badges: start -->
<!-- badges: end -->

The goal of skewsamp is to provide access to sample size estimation
methods for group comparisons where the underlying data are skewed and
thus violate the assumptions for common methods of sample size estimation. 

In particular, skewsamp offers an approach based on generalized linear
models (GLM) as described by Cundill & Alexander (2015) and an approach
based on the nonparametric Wilxocon-Mann-Whitney test in the location 
shift paradigm as described by Chakraborti, Hong, & van de Wiel (2006).

## Installation

You can install the package using the binary file 
`build/skewsamp_1.0.0.tgz` with the following command:

``` r
install.packages("<path-to-binary>/skewsamp_1.0.0.tgz", repos = NULL, type = "binary")
```

## Example 1

Sample size determination in the GLM approach for gamma-distributed
data:

```{r example}
library(skewsamp)
skewsamp::n_gamma(mean0 = 1, effect = 0.5, shape0 = 1, alpha = 0.05, power = 0.9)
```

## Example 2

Sample size determination in the location shiftb approach. This approach
requires pilot data, which we draw from an exponential distribution for
the sake of the example:

```{r example2}
library(skewsamp)
skewsamp::n_locshift(s1 = rexp(10), s2 = rexp(10), delta = 0.5, alpha = 0.05, power = 0.9)
```

# References

- Cundill, B., & Alexander, N. D. E. (2015). Sample size calculations for skewed distributions. BMC Medical Research Methodology, 15(1), 1–9. https://doi.org/10.1186/s12874-015-0023-0
- Chakraborti, S., Hong, B., & Van De Wiel, M. A. (2006). A note on sample size determination for a nonparametric test of location. Technometrics, 48(1), 88–94. https://doi.org/10.1198/004017005000000193
